### 2015-01-10 mcmc.tex
autocorrelation

...Making this heuristic condition more precise
...Autocorrelation time is the premier tool
...How is Autocorrelation time defined?
...How is Autocorrelation time measured?
...Why is it is not a panacea? ...estimators ...getting stuck in one mode

>>>>

The above heuristics can be made more precise (in terms of the amount
of deviation one expects between the means and variances, say, of two
disjoint subsets of the chain.
The premier tool for making this heuristic precise, however, is to
look at the \emph{autocorrelation time} of the chain.
In general, when one has a sequence $(\pars_1, \pars_2, \theta_3, \cdots)$
generated by a Markov Process in the $\pars$ space, nearby points in
the sequence will be similar, but sufficiently distant points will not
``know about'' one another;
the autocorrelation function measures this.

The autocorrelation function is defined by
\begin{equation}
C(\Delta) &\equiv& \frac{E[(\pars_t - \mu)\,(\pars_{t+\Delta} - \mu)]}{E[(\pars_t)^2]
\\
\mu &=& E[\pars_t]
\quad ;
\end{equation}
that is, it is the covariance of points separated by $\Delta$, taken
relative to the variance.
By construction
\begin{equation}
C(0) &=& 0
\\
\lim_{\Delta\rightarrow\infty} C(\Delta) &=& 0
\quad ,
\end{equation}
and by definition, the autocorrelation ``time'' $\tau$ is
\begin{equation}
\tau = \int C(\Delta)\,\dd\Delta
\quad .
\end{equation}
Heuristically, the autocorrelation time is the number of samples you
need to take before you get an independent sample.
More precisely, the autocorrelation time is the factor by which you
have to reduce the number of samples when you compute the variance on
a sampling-based expectation value estimate.\note{HOGG Explain more fully.}

Of course, the autocorrelation-time definition does not by itself provide
an \emph{estimator} for the time.

...Why is it is not a panacea? ...estimators ...getting stuck in one mode
